\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-08-23 docs/papers/sto/so.tex
FIXUP draft minor

  and $g$ (along axis and face diagonal) at 3 different $a$'s; Track
  mean epoch loss
\item (train) Randomize snapshots of each simulation instead of
  sequential; alternatively accumulate their gradients; Normalize loss
  by number of time steps\newline
  \YZ{\textbf{Update}: Normalizing loss by number of time steps seems to halt
  the training of late time snapshots, i.e. they stop improving.}

@@

We perform distributed data-parallel training using GPU devices hosted on
multiple CPU nodes.
% TODO hardware details
The 512 training data samples are uniformly distributed to the processes, with
each process being binded to a single GPU device.
In each training step, a data sample is fed into the GPU from the CPU memory
where the preloading takes place to save the reading time from the disk.

>>>>

  and $g$ (along axis and face diagonal) at 3 different $a$'s

@@

We perform distributed data-parallel training using GPU devices hosted on
multiple CPU nodes.
% TODO hardware details
The training data samples are uniformly distributed to the processes, with
each process being binded to a single GPU device.
In each training step, a data sample is fed into the GPU from the CPU memory
where the preloading takes place to save the reading time from the disk.
